A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-10-01 bioc-workflow.tex
contributions, competing interests

\textbf{TODO} In order to give appropriate credit to each author of an
article, the individual contributions of each author to the manuscript
should be detailed in this section. We recommend using author initials
and then stating briefly how they contributed.

@@

No conflict of interest.

@@

L.M.B is supported by a Wellcome Trust Technology Development Grant
(grant number 108467/Z/15/Z). L.G. is supported by the BBSRC Strategic
Longer and Larger grant (Award BB/L002817/1).

>>>>

All authors developed the software presented in this workflow and
wrote and approved the manuscript.

@@

The authors declare that they have no competing interest.

@@

LMB is supported by a Wellcome Trust Technology Development Grant
(grant number 108467/Z/15/Z). LG is supported by the BBSRC Strategic
Longer and Larger grant (Award BB/L002817/1).
